POMDP comparisons across sigma_m, sigma_g

### 2018-01-31 appendix/appendix_recruit_first.Rmd
don't render recruit_first v of appendix
not sure why is failing on drone, but should fix drone builds.

@@

ggplot2::theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_recruit_harvest" # Store the computed solution files here

>>>>

```{r include = FALSE}
## Not in use, turn rendering off
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, eval=FALSE)
```

@@

ggplot2::theme_set(theme_bw())
options(mc.cores=parallel::detectCores())
log_dir <- "../data/observe_recruit_harvest" # Store the computed solution files here
